Of judges, aliens and total preorders

### 2021-02-01 paper/1901_3230880_philip_heltweg.tex
fix: more feedback

% TODO: QUESTION: consider not having a table of contents
\tableofcontents

@@

@@

\subsection{Belief sets and epistemic states}
% TODO QUESTION: explain contraction, revision, expansion?
% TODO: Gardenfors correct? read!
A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}. Alchourrón, Gärdenfors, and Makinson (AGM theory, \cite{Alchourron1985}) define postulates for belief sets and their contraction, expansion or revision with new evidence. In the process of belief revision an agent keeps their set of beliefs consistent while incorporating new information, even if it is inconsistent with the current belief set \cite{Gaerdenfors1984}. Darwiche and Pearl \cite{Darwiche1997} argue that working with belief sets is not expressive enough for satisfying results in iterated belief revision. They make the distinction between propositional beliefs (beliefs the agent accepts and are part of the belief set) and conditional beliefs as beliefs the agent is prepared to adopt with new evidence.

@@

% TODO QUESTION: do we need to discuss this in ore detail? faithful assignment here:
%Katsuno and Mendelzon [17] propose that an epistemic state Ψ
%should be equipped with an ordering ≤Ψ of the worlds (interpretations), where the compatibility with Bel(Ψ) is ensured by the socalled faithfulness.
%Definition 1 (Faithful Assignment [17]) A function Ψ 
%→≤Ψ that
%maps each epistemic state to a total preorder on interpretations is
%said to be a faithful assignment if and only if:
%(FA1) if ω1 ∈ Ψ and ω2 ∈ Ψ, then ω1 Ψ ω2
%(FA2) if ω1 ∈ Ψ and ω2 ∈  / Ψ, then ω1 <Ψ ω2
%Intuitively, ≤Ψ orders the worlds by plausibility, such that the minimal worlds with respect to ≤Ψ are the most plausible worlds.

@@

While DP-AGM define the most plausible worlds after a revision by $\alpha$ (as $min(\alpha, \leq_{\mathbb{E}})$), Darwiche and Pearl also define postulates that restrict the rest of the new ordering. Since this synopsis only focused on the revision of tpos, the semantic (i.e. in terms of how the ordering of worlds undergoes change) versions are shown here. For more details and sentential versions refer to \cite{Darwiche1997}.

@@

% TODO QUESTION: we probably need to make clearer that this is where the paper starts, caro thought it should be in 2.x
\section{Additional metadata for tpo revision}
\subsection{Enriching epistemic states}
Based on DP-AGM and the postulates $(CR1)$-$(CR4)$, Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering. The goal of their paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. These functions are referred to as revision operators for $\leq$.

@@

Since this synopsis focuses on the revision of tpos itself, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here. For a more detailed explanation of the operator, SPHs or their properties refer to \cite{Booth2011}.

@@

% TODO QUESTION: this critique example seems very weak
Considering the quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened. Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not. Consider the following situation in our courtroom example \ref{example:example-introduction}: New evidence $\alpha$ arrives that fingerprints of John have been found at the place of the murder. $\alpha$  makes a world $x$, with $p$ being true, more likely. But, because of a large body of evidence, the judge still considers a world $y$, where Mary is the murderer, to be more plausible. This means there can be no evidence $\gamma$ that would make the agent consider the world $x$ more likely than $y$ according to \ref{AST7}:

>>>>

\tableofcontents

@@

% TODO: put text here

@@

\subsection{Belief sets and epistemic states}
\label{chapter:belief-sets-and-epistemic-states}
% TODO: explain contraction, revision, expansion
% ANSWER: Ich würdes es ganz kurz erläutern im Text. Im Vortrag vielleicht nicht umbedingt.

% TODO: Gardenfors correct? read!
A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}. Alchourrón, Gärdenfors, and Makinson (AGM theory, \cite{Alchourron1985}) define postulates for belief sets and their contraction, expansion or revision with new evidence. In the process of belief revision an agent keeps their set of beliefs consistent while incorporating new information, even if it is inconsistent with the current belief set \cite{Gaerdenfors1984}. Darwiche and Pearl \cite{Darwiche1997} argue that working with belief sets is not expressive enough for satisfying results in iterated belief revision. They make the distinction between propositional beliefs (beliefs the agent accepts and are part of the belief set) and conditional beliefs as beliefs the agent is prepared to adopt with new evidence.

@@

% TODO QUESTION: do we need to discuss this in ore detail? faithful assignment here:

% ANSWER: Das ist eine gute Frage. So wie ich das Paper von Booth und Meyer im
% Kopf habe werden dort die Ordnung mit epistemischen Zuständen
% gleichgesetzt (was Darwiche und Pearl ja nicht machen). Von daher halte
% ich das für ok es nicht im aller formalen Ausführlichkeit zu machen.
% Aber man könnte es im einen Satz erwähnen.

%Katsuno and Mendelzon [17] propose that an epistemic state Ψ
%should be equipped with an ordering ≤Ψ of the worlds (interpretations), where the compatibility with Bel(Ψ) is ensured by the socalled faithfulness.
%Definition 1 (Faithful Assignment [17]) A function Ψ 
%→≤Ψ that
%maps each epistemic state to a total preorder on interpretations is
%said to be a faithful assignment if and only if:
%(FA1) if ω1 ∈ Ψ and ω2 ∈ Ψ, then ω1 Ψ ω2
%(FA2) if ω1 ∈ Ψ and ω2 ∈  / Ψ, then ω1 <Ψ ω2
%Intuitively, ≤Ψ orders the worlds by plausibility, such that the minimal worlds with respect to ≤Ψ are the most plausible worlds.

@@

The DP-AGM postulates put restrictions how the belief set of an agent changes after revision of new evidence $\alpha$. As outlined before belief sets can be extracted from epistemic states by taking the set of formulae true in all most plausible worlds after revision by $\alpha$, defined as $\modelsOf{B(\mathbb{E}\ast\alpha)} = min(\alpha, \leq_{\mathbb{E}})$.

Darwiche and Pearl also define postulates that restrict how the rest of the new ordering changes. This extends the constrains to not only the changes in the currently held belief of an agent (the belief set), but also to the conditional beliefs it is prepared to accept depending on future evidence. Since this synopsis only focused on the revision of tpos, the semantic (i.e. in terms of how the ordering of worlds undergoes change) versions are shown here. For more details and sentential versions refer to Darwiche and Pearl \cite{Darwiche1997}.

@@

\section{Additional metadata for tpo revision}
% TODO: Text, put in that paper by booth and meyer starts here basically
\subsection{Enriching epistemic states}
Based on DP-AGM and the postulates $(CR1)$-$(CR4)$, Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering. The goal of their paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. These functions are referred to as revision operators for $\leq$.

@@

Since this synopsis focuses on the revision of tpos itself, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here. For a more detailed explanation of the operator, SPHs or their properties refer to Booth and Meyer \cite{Booth2011}.

@@

% TODO: this critique example seems very weak
Considering the quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened. Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not. Consider the following situation in our courtroom example \ref{example:example-introduction}: New evidence $\alpha$ arrives that fingerprints of John have been found at the place of the murder. $\alpha$  makes a world $x$, with $p$ being true, more likely. But, because of a large body of evidence, the judge still considers a world $y$, where Mary is the murderer, to be more plausible. This means there can be no evidence $\gamma$ that would make the agent consider the world $x$ more likely than $y$ according to \ref{AST7}:
